% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

% Typography
\usepackage{fontspec,realscripts}
\setmainfont[Ligatures=TeX,Numbers=OldStyle]{Minion Pro}
\setsansfont[Ligatures=TeX]{Myriad Pro}
\setmonofont[Scale=MatchLowercase]{Menlo}
\frenchspacing
\usepackage{titlesec}
\titleformat{\section}
  {\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}
  {\em}{\normalfont\thesubsection}{1em}{}
\titleformat{\subsubsection}
  {\em}{\normalfont\thesubsubsection}{1em}{}

% Hyperref
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref}
\hypersetup{%
  breaklinks=true,
  colorlinks=true,
  urlcolor=BrickRed,  % for external links
  linkcolor=NavyBlue, % for normal internal links
  pdftitle={TUCFA Constitution, 21 May 2015},
  pdfauthor={Tyndale University College Faculty Association},
  pdfcreator={FA Secretary-Treasurer}}
\urlstyle{same} % don't use monospace font for urls

\title{Constitution of the\\Tyndale University College\\Faculty Association}
\author{%
  Web: \href{http://tucfa.ca/}{tucfa.ca}\\
  Email: \href{mailto:fa@tucfa.ca}{fa@tucfa.ca}
}
\date{%
  As amended at the General Meeting of 21 May 2015
}

\begin{document}
\maketitle
\tableofcontents

\section{Name}

This Association shall be called the Tyndale University College Faculty Association (TUCFA).

\section{Purpose of the TUCFA}

\begin{enumerate}
\item
To advance teaching, scholarship, research, and service within the mission statement of the University College;
\item
To represent all employees of the University College who are eligible for full membership in the Association in all matters of employer-employee relations including salaries, pensions, work load, and working conditions;
\item
To deal with items of common interest to faculty members relating to the University College or to the broader interests of the academic community;
\item
To encourage cooperation between the teaching faculty of this University College and the teaching faculty of other universities, colleges, and seminaries.
\end{enumerate}

\section{Affiliations}

Members of the Faculty Association may be affiliated with the Canadian Association of University Teachers (CAUT).

\section{Membership}

\subsection{Full Membership}

Full membership in the Association is open to all full-time members of the teaching faculty of Tyndale University College, including the Library director and administrative faculty exclusive of those who sit on cabinet, as well as those faculty teaching at least four courses per academic year.

\subsection{Associate Membership}
Retired members of the TUCFA who continue to be employed by the institution may be associate members. Associate members will have no power to vote, and are not eligible for membership on the Executive Committee.

\subsection{Continuation}
Membership may continue until employment with the University is terminated; or until a change of status results in ineligibility for TUCFA membership.

\subsection{Withdrawal}
Any member may withdraw from membership upon written notice to the President of the Association.

\subsection{Establishment and Suspension}

Membership shall be established by the payment of dues of those eligible (\$100.00 per annum for full members, \$1.00 per annum for associate members). Failure to pay dues for a period of six months will result in suspension of membership.

\section{Dues}

The annual dues are set out at the Annual General Meeting held in May of each year. The call shall be for dues to cover the next academic year, payable in most cases before 1 December.

\section{Executive Committee of the TUCFA}

\subsection{Elected Officers}
The Executive Committee of the TUCFA shall consist of three elected officers: the President, the Vice-President, and the Secretary-Treasurer.

\subsection{Annual Election}
An election to fill vacancies among the elected officers shall be held at the Annual General Meeting. Newly elected members shall assume office at the close of the Annual General Meeting. Preceding the election, a nominating committee shall actively seek nominations from the general membership and shall endeavour to secure a list of nominees broadly representative of the membership.

\subsection{Eligibility}
Only full members of the Association are eligible for election to the Executive Committee. Any member of the Executive Committee who assumes administrative or managerial duties during his or her term of office, which would make him or her ineligible for election pursuant to this clause, shall be deemed thereby to have resigned from the Executive.

\subsection{Terms of Office}
The terms of office for elected members of the Executive Committee shall be as follows:

\begin{enumerate}
\item
President --- one year
\item
Vice-President --- one year
\item
Secretary-Treasurer --- one year
\end{enumerate}

\subsection{Compensation}
No honoraria shall be paid by the Association to any member of the Executive Committee.

\subsection{Re-election}
All members of the Executive are eligible for re-election at the expiration of their term of office. Executive members shall not serve for more than three consecutive years, unless there are no other candidates for the position, or unless they are elected by the votes of at least two-thirds of the members present at the Annual General Meeting.

\subsection{Vacancies on the Executive Committee}

\subsubsection{By-elections}
\label{by-elections}
Should an elected member of the Executive Committee resign or be unable to continue in office for any reason, a by-election shall be held to elect a replacement for the unexpired term of office of that member within 30 days of the occurrence of the vacancy.

\subsubsection{Succession}
Should the Presidency become vacant during the President's term of office, the Vice-President shall act as President until a by-election is held.

\subsubsection{Removal of One or More Officers}
\label{remove-one}
At a duly constituted General Meeting of the Association, any or all of the elected members of the Executive Committee may be called upon to resign by a motion passed by a two-thirds majority of the full members present and eligible to vote, provided that any notice of motion appears on the written agenda circulated 48 hours in advance of the meeting. The members of the Executive Committee identified in the motion shall then be held to have resigned, and the provisions of \ref{by-elections} shall hold, except as specified in \ref{remove-more} below.

\subsubsection{Removal of More Than One Officer}
\label{remove-more}

In the event that a motion passed as in \ref{remove-one} above requires the resignation of more than one of the elected members of the Executive Committee, a mail (or e-mail) ballot on that motion shall be held without delay. If the motion is then passed by a simple majority of those members voting, the Past President (or designate) shall, within ten days, call and chair a special General Meeting of the Association. This meeting shall elect an interim Executive Committee, which committee shall appoint a nominating committee within seven days, and proceed to hold an election for a new Executive Committee, using the procedures as specified in the Constitution.

\subsubsection{Interim Officers}
Should it be necessary to fill a position on the Executive Committee on an interim basis pending an election or by-election, the Executive Committee shall do so, informing the general membership of its action forthwith.

\subsection{Duties of Officers}

\subsubsection{The President}

\begin{enumerate}
\item
Supervises the general management of the affairs of the Association and implements the policies set by the Association and the Executive Committee;
\item
Presides at meetings of the Executive Committee and at TUCFA General Meetings;
\item
Shall have the power to take all necessary steps of an emergency nature for the benefit of the Faculty Association when specifically authorized by special session of the Executive Committee. If an emergency session of the Executive Committee cannot be summoned, the President may take steps of an emergency nature, but must report such actions, as soon as possible, to the Executive Committee and thereafter to the general membership.
\end{enumerate}

\subsubsection{The Vice-President}

\begin{enumerate}
\item
Fulfills any duties assigned by either the President or the Faculty Association Executive Committee.
\item
Stands in for the President when he or she is ill or unavoidably absent.
\end{enumerate}

\subsubsection{The Secretary-Treasurer}

\begin{enumerate}
\item
Fulfills any duties assigned by either the President or the Faculty Association Executive Committee;
\item
Issues notices and agendas for meetings of the Faculty Association Executive Committee and for General Meetings of the Faculty Association at the times and in the manner specified;
\item
Maintains the minute books for meetings of the Faculty Association Executive Committee and for General Meetings of the Faculty Association;
\item
Shall circulate a copy of the minutes of all TUCFA General Meetings to members in good standing, and ensure that copies of the minutes of the Executive Committee meetings are accessible to members, upon request.
\item
Shall be responsible for the care and custody of funds and assets of the Faculty Association according to the usual practice and shall regularly consult with the President and the President-Elect;
\item
At each Annual General Meeting of the Faculty Association shall present an account of the Faculty Association's finances, and an appropriate budget for the TUCFA for the forthcoming year, together with any recommendations for changes in the fee structure;
\item
Shall maintain books of account and make these available for inspection to the members of the Faculty Association on request.
\end{enumerate}

\subsubsection{The Executive Committee}

\begin{enumerate}
\item
Shall carry into effect all resolutions of General Meetings of the Faculty Association and generally manage its affairs and finances;
\item
Is empowered to form sub-committees and ad hoc committees, which are directly responsible to the Executive Committee;
\item
Shall meet at the request of the President or at the request of two of its members, upon reasonable notice of meeting;
\item
Shall consider matters of a substantive nature brought to it by at least a simple majority of the Association and shall bring the matter, together with its recommendation, to the next General Meeting.
\end{enumerate}

\section{Committees}

Standing Committees may only be established or abolished by a two-thirds majority vote at a TUCFA General Meeting, following due notice of motion on the agenda.

\section{Meetings}

\subsection{General, Executive, and Emergency}
General Meetings of the TUCFA and meetings of the Executive Committee may be called at any time by the President. Emergency meetings also may be called by the President. Decisions taken at an Emergency meeting must be ratified by a quorum present at a subsequent meeting, the agenda of which must be circulated not less than 48 hours after the Emergency meeting. The agenda for such meetings are prepared by the Secretary-Treasurer in consultation with the President and Vice-President and circulated to the appropriate membership.

\subsection{Requests for Meetings}
The President must call a meeting of the Faculty Association upon receipt of a written request to that effect, signed by at least five members stating the reason for which the meeting is desired.

\subsection{Annual Meetings}
There shall be at least two General Meetings of the TUCFA per year, at which time the Executive Committee shall report on its activities to the membership. One of these meetings shall be the Annual General Meeting of the TUCFA.

\subsection{Order}
The meetings will be conducted according to \emph{Robert's Rules of Order} unless otherwise specified in this Constitution.

\section{Quorum}

\subsection{Executive Committee}
Two members of the Executive Committee, one of whom must be the President, shall form a quorum for an Executive Committee meeting.

\subsection{General Meetings}
A simple majority of the full members of the TUCFA shall form a quorum for a TUCFA General Meeting.

\section{Voting}

\subsection{Chairperson}
The chairperson of a meeting of the Executive Committee shall have a regular vote. In the case of a tie vote, the motion shall be held to fail and the \emph{status quo} shall prevail.

\subsection{Secret Ballot}
Voting shall be by secret ballot if so requested by the majority of members present at any Faculty Association meeting.

\subsection{By E-mail}
In the event of an emergency, as determined by a quorom of the Executive Committee, an e-mail vote may be taken on the question(s) at hand.

\section{Amendments to the Constitution}

At least one week's notice of proposed amendments must be given in writing through the Secretary-Treasurer. After due discussion at a General Meeting and providing two-thirds of members present and voting concur, the Constitution may be amended by a majority of those voting.

\begin{itemize}
\item
Ratified 17 November 2005
\item
Amended 21 May 2015
\end{itemize}

\end{document}
